A community-maintained standard library of population genetic models

### 2019-12-20 popSimManu.tex
some reworking of intro
fixed typo

software->library

For these reasons, we have generated a standardized, community-driven resource
for simulating published demographic models from a number of popular study systems.
This resource, which we call \stdpopsim, makes running
realistic simulations for population genetic analysis a simple matter of
choosing pre-implemented models from a community-maintained catalog, 
The \stdpopsim catalog currently contains three organisms: humans,
\emph{Drosophila~melanogaster}, and \emph{Arabidopsis~thaliana}. For each
organism the catalog contains details on the physical organization (e.g., chromosome structure)
of their genomes, one or more genetic maps, default population-level parameters (mutation rate,
generation time) and one or more published demographic histories. Through
either a command line interface or a simple Python API, users can specify which
organism, genetic map, chromosome, and demographic history they are interested in simulating, and the
simulation output from their chosen model is returned.
In this way, \stdpopsim will enable rigorous evaluation of population genetic software,
and contribute to increased reliability of population genetic inferences.

The \stdpopsim software has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its quality.
Importantly, we have rigorous quality control methods to ensure implemented models are accurate
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community.
Below we describe the resource and give
examples of how it can be used to benchmark demographic inference methods.

>>>>

For these reasons, we have generated a standardized, community-driven resource
for simulating published demographic models from a number of popular study systems.
This resource, which we call \stdpopsim, makes running
realistic simulations for population genetic analysis a simple matter of
choosing pre-implemented models from a community-maintained catalog.
The \stdpopsim catalog currently contains three organisms: humans,
\emph{Drosophila~melanogaster}, and \emph{Arabidopsis~thaliana}. For each
organism the catalog contains details on the physical organization (e.g., chromosome structure)
of their genomes, one or more genetic maps, default population-level parameters (mutation rate,
generation time) and one or more published demographic histories. Through
either a command line interface or a simple Python API, users can specify which
organism, genetic map, chromosome, and demographic history they are interested in simulating, and the
simulation output from their chosen model is returned.
In this way, \stdpopsim will enable rigorous evaluation of population genetic software,
and contribute to increased reliability of population genetic inferences.

The \stdpopsim library has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its quality.
Importantly, we have rigorous quality control methods to ensure implemented models are accurate
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community.
Below we describe the resource and give
examples of how it can be used to benchmark demographic inference methods.
